Diagnoses and cell types

### 2025-10-08 analyses/infercnv-consensus-cell-type/exploratory-notebooks/reference-query-counts.Rmd
typo

Note that we are including multiplexed libraries from project `SCPCP000009` here as well; 12 libraries from that project from are eligible, and all but of of those are multiplexed.
These libraries would effectively be using pooled references in `inferCNV`, since we did not demultiplex libraries.

>>>>

Note that we are including multiplexed libraries from project `SCPCP000009` here as well; 12 libraries from that project from are eligible, and all but one of those are multiplexed.
These libraries would effectively be using pooled references in `inferCNV`, since we did not demultiplex libraries.
